---
title: "Prediction Assignment Writeup"
author: "Adugna"
date: "February 22, 2021"
output: html_document
---

The goal of this project is to predict the manner in which people did the exercise.

The data for this project come from this source: http://groupware.les.inf.puc-rio.br/har.

## Pre-processing Data
First, we need to clean up the data by deleting the fields that do not have any value. In addition, we also delete the first 7 columns: X, user_name, raw_timestamp_part_1, raw_timestamp_part_2, cvtd_timestamp, new_window, num_window. These features are obviously not related to predict the outcome.

```{r}
library(caret)
set.seed(12463)

training <- read.csv("pml-training.csv", stringsAsFactors=FALSE)
training$classe <- as.factor(training$classe)
training <- training[,-nearZeroVar(training)]
training <- training[,-c(1,2,3,4,5,6,7)]

```


Here, we use KnnImpute method to remove NA values. Also, we use PCA to standardize and reduce features.

```{r}
inTrain <- createDataPartition(y=training$classe, p=0.75, list=FALSE)
training <- training[inTrain,]
testing <- training[-inTrain,]

preObj <- preProcess(training[,-length(training)],method=c("center", "scale", "knnImpute", "pca"), thresh=0.9)
clean_data <- predict(preObj,training[,-length(training)])
```

## Prediction

Using Knn method to build model and test data to evaluate the performance of our model.

```{r}
modelFit <- train(training$classe ~.,data=clean_data, method="knn")
test <- predict(preObj, testing[,-length(testing)])
confusionMatrix(testing$classe, predict(modelFit,test))
```


Load the testing data and predict:

```{r}
testing <- read.csv("pml-testing.csv", stringsAsFactors=FALSE)
testing <- testing[,names(testing) %in% names(training)]

test <- predict(preObj, testing)
predict_result <- predict(modelFit, test)
```
